---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# researchr
RMarkdown templates for research design documentation.

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

## Installation

```{r, eval = FALSE}
# Install release version from CRAN
install.packages("researchr")
# Install development version from GitHub
devtools::install_github("andrewcstewart/researchr")
```

## Usage

```{r, eval = FALSE}
# Run once to configure your project to use researchr
researchr::use_researchr()
```

## Overview

The primary purpose of `researchr` is to aid in the design of research projects, particularly data science projects, by offering a lightweight composable frameork of document templates and functions to track and manage a research design throughout the course of its history.

The emergence of the data science Notebook and its ensuing ecosystem of tutorials tends to create the impression that data science can always be captured in a concise, linear sequence of steps within a single session. It makes sense for those tutorials to consist of single notebooks rather than require readers to reference a series of separate notebooks, but in practice real life is much more messy. Research projects typically span long lengths of time, attempt several different approaches and combinations of approaches, and iteratively build off of each previous version of work. A more accurate picture might be a network of notebooks ; and that's basically what `researchr` is.

There's a couple key features that `researchr` offers to improve the scientist's quality of life:

1. Breaks down research projects into a few different interrelated components, which affords more flexibility in terms of conceptual composition of procedures and aids in more deliberative design of your research.
2. Removes the distraction of naming and organizing your folder structure, which is by far the most challenging problem in data science.
3. Structures the otherwise unstructured world of research code without imposing overly complex and burdensome software frameworks.

There are plenty of tools out there to help data science projects including workflow managers, data versioning tools, metric collectors, reproducibility automation, etc. `researchr` doesn't attempt to do any of those things, but it should compliment any choice of those tools nicely.

At its core, the package consists of two primary components:

1. RMarkdown templates for protocols and designs.
2. Functions and metadata for managing the research design.

## Research Design

The research design itself consists simply of an RStudio project and some `yaml` encoded metadata files, as well as RMarkdown files that document the research. 

### Document types

- **data protocols** document how your data is collected and abstract this step away from downstream analysis.
- **method protocols** make up the bulk of your project and generally consist of various analyses.
- **instrumentation designs** describe any algorithms or workflows that are frequently used throughout your project.
- **experimental designs** organize a series of experiments using methods and instruments to generate evaluation reports.
- **prototype designs** are useful for documenting the output of your research, whether that be for some form of product feature or advisory report.

### Functions

- `use_researchr`
- `new_research`
- `add_data`
- `add_method`
- `add_instrument`
- `add_experiment`
- `add_prototype`
- `_design_inventory` - traverses the directory tree to generate an inventory of current design state.
- reference functions (ie, `here` for "M-1")
- id generators
- plot the design graph
- generate design table (data.frame)

## Likely requirements 

- `fs`
- `yaml`
- `DiagrammR`


## Frequently Asked Questions 


